%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{verbatim}  % to use comment line \begin{comment} \end{comment}
\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0.0in]{geometry} % Document margins
\usepackage{hyperref} % For Hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=cyan,      
    urlcolor=blue
}
\urlstyle{same}

\renewcommand{\baselinestretch}{1.0}
\name{Sahil Jain} % Your name
\address{700 Health Sciences Drive, Chapin C 1044B, Stony Brook, New York 11790} % Your address
\address{
(631)~$\cdot$~542~$\cdot$~3812 \\
\href{mailto:sahjain@cs.stonybrook.edu}{sahjain@cs.stonybrook.edu}\\       
\href{http://www.linkedin.com/in/sahil2441}{www.linkedin.com/in/sahil2441}\\  
\href{http://www.github.com/sahil2441}{www.github.com/sahil2441}
} 


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}
{Stony Brook University $\bullet$ New York, U.S.A.} {\emph{Fall 2015 -- Dec 2016} }
{Master of Science, Computer Science } {} 
Courses: Analysis of Algorithms, Operating Systems, Computing with Logic, Compiler Design, Fundamentals of Computer Networks, Fundamentals of 
Data Science, Modelling and Simulation.
\end{rSubsection}

\begin{rSubsection}
{Indian Institute of Technology, Roorkee $\bullet$ Roorkee, India} {\emph{Fall 2009 -- May 2014}}{Integrated Master of Science, Applied Mathematics} {} 
\item[] 
{{Thesis: \href{http://sci-edit.net/journal/index.php/cgt/article/download/40/35}{Fama French Three Factor Model in Indian Stock Market} }}  \\
%{{Research Publication: \href{http://www.iosrjournals.org/iosr-jbm/papers/vol2-issue1/A0210104.pdf?id=5531}{Analysis of Equity Based Mutual Funds in India} }} \\
Courses: Computer Systems and Programming, Database Management, Data Structures, Graph Theory, Number Theory, Discrete Mathematics.

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Java, C/C++, Python, Prolog
 \\
 Google Technologies & Google App Engine, Tradefed, Bigtable, Protocol Buffer
 \\
Databases & MySQL, Oracle 
\\
Tools & SVN, Git, Android Studio, Eclipse, Gradle, JDeveloper, Matlab, R
 \\
Technologies & JSP, Servlets, JDBC,  Eclipse, ADF, WebLogic, Tomcat, JIRA.
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

%------------------------------------------------

\begin{rSubsection}{Google Inc.}{\emph{ May. 2016 -- August 2016}}{Software Engineer, Tools and Infrastructure Intern}{Mountain View, CA}
\item Working with Android's Vendor Test Suite (VTS) team to achieve the mission : `Next Billion Users'.
\item Developed a Host-Driven Test Type (TradeFed, Java) , Result Parser (TradeFed, Java) and a Callable Handler Server (Python).
\item Developed a Dashboard for Android O that integrates the above Framework using Google App Engine, Protocol Buffer and Bigtable, leading to increase in performance and security.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Trip Tracker -- Android App}{\emph{ Jan. 2015 -- August 2015}}{Founder, Developer}{Mumbai, India}
\item Developed an Android Application {\emph{Trip Tracker}} that tracks user's  location and notifies friends based on location coordinates. 
Technologies Used: Java, Android Studio, Google Maps API, Google Cloud Messaging (GCM), Facebook Authentication API. \\
\href{https://github.com/sahil2441/Trip-Tracker}{GitHub Link}
{\tiny$\bullet$}
\href{https://play.google.com/store/apps/details?id=me.sahiljain.tripTracker}{Play Store Link}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Oracle Financial Services Software} {\emph{Sept. 2014 -- June 2015}} {Applications Developer}
{Mumbai, India}

\item Developed a series of Taskflows and APIs for Oracle Banking Platform -- a next generation Banking Solution, leading to an increased security in the product.\\
Technologies and Languages: Java, Jdeveloper, ADF, JSFF, Servlets, JSP, WebLogic, Tomcat, JDBC, \\
Eclipselink, Service Oriented Architecture, JIRA.

\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	Projects SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects {$\bullet$} \emph{\href{http://www.github.com/sahil2441}{\footnotesize Github Handle(sahil2441)}}}


%----------------------------------------------------------------------------------------
% Nachos OS
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Nachos Operating System} {\emph {Aug. 2015 -- Dec. 2015}}{}{}
\item Extended Nachos OS to implement System Calls, Synchronisation Primitives and Scheduling Algorithms.
\item Improved File System by implementing File Extension, Directory Structure, Single and Double Indirect Block.
\item Extended Nachos to support Demand Paged, Memory Mapped Files by adding new System Calls : Mmap() and Munmap().
{\tiny$\bullet$}
\href{https://github.com/sahil2441/Nachos-Operating-System}{GitHub Link}
\end{rSubsection}

%----------------------------------------------------------------------------------------
% Mininet
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Network Topology using Mininet}{\emph{March 2016 - April 2016}}{}{}
\item Implemented Custom Network Topology using Mininet and Quagga to set up Static Network Routes. \\
\href{https://github.com/sahil2441/FCN-Projects}{GitHub Link}
\end{rSubsection}

%----------------------------------------------------------------------------------------
% DNS - FCN
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Domain Name Server Resolver} {\emph {Jan. 2016 - Feb. 2016}}{}{}
\item Implemented a DNS Resolver in Java that resolves DNS query to provide IP address.
\item Used Round Robin Scheduling Algorithm to choose which root server to access. {\tiny$\bullet$}     
\href{https://github.com/sahil2441/FCN-Projects}{GitHub Link}
\end{rSubsection}

%----------------------------------------------------------------------------------------
% Compiler
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Compiler for Java type language} {\emph {Feb. 2016 -- May 2016}}{}{}
\item Designed and build a compiler in Python for Java type language that includes different phases of compiler design, such as  
Lexical Analysis, Syntax Analysis, Semantic Analysis, IR Code generation, Code Optimizations, and Final Machine Code Generation.
{\tiny$\bullet$}
\href{https://github.com/sahil2441/Compiler}{GitHub Link} 
\end{rSubsection}


%----------------------------------------------------------------------------------------
% Prolog
%----------------------------------------------------------------------------------------

%\begin{rSubsection}{Projects in Prolog }{\emph{Aug. 2015 -- Dec. 2015}}{}{}
%\item Performed Resolution operations and Herbrand Models in XSB, SWIPL variant of Prolog. Tools: XSB, Swi-Pl, Prolog Development Tools.
%\href{https://github.com/sahil2441/Prolog-Problems}{GitHub Link}
%{\tiny$\bullet$}
%\href{http://stackoverflow.com/users/2733964/sahil-jain}{Stackoverflow Link}
%\end{rSubsection}

%----------------------------------------------------------------------------------------
% Yelp
%----------------------------------------------------------------------------------------

%\begin{rSubsection}{Yelp Reviews Based Data Analysis }{\emph{Aug. 2015 -- Dec. 2015}}{}{}
%\item Conducted an analysis on 1.6 M yelp review that included Sentiment Analysis, Correlation plots, Calendar
      %and World Heat maps.  Tools: MySQL, Tableau, Stata, Excel, Matlab, Java. 
%\href{https://drive.google.com/file/d/0BzgUxxyAUxkycTZsY0pUUXY0NmM/view?usp=sharing}{Project Report}
%\end{rSubsection}

%----------------------------------------------------------------------------------------
% NYC Open Data
%----------------------------------------------------------------------------------------

%\begin{rSubsection}{NYC Open Data Analysis  }{\emph{Aug. 2015 -- Dec. 2015} }{}{}
%\item Performed Chi Squared test, Hypothesis tests, Multiple Regression analysis on data sets from NYC Open
%      Data. Tools: MySQL, Stata, Excel, Matlab, Java.
%     \href{https://drive.google.com/file/d/0BzgUxxyAUxkyZTRlVE9xZVR6NDg/view?usp=sharing}{Project Report}
%\end{rSubsection}
%----------------------------------------------------------------------------------------


\end{rSection}

\end{document}
